---
title: "Analysis of pilot data 6 for genex"
output: github_document
---

[Link to expt](https://www.mit.edu/~karengu//category-experiment/template/template.html)
[Other condition](https://www.mit.edu/~karengu/category-experiment2/category-experiment/template/template.html)

```{r, echo = F}
knitr::opts_chunk$set(echo = F, warning = F, fig.width = 6,
                      fig.height =4, fig.asp = 0.5)
library(knitr)
library(ggthemes)
library(tidyboot)
library(jsonlite)
library(tidyverse)
theme_set(theme_few())
results.path <- "../results/anon_results_v6/"
# fig.path <- "~/projects/negant/"
```

```{r, echo=F, warning=F}

anon_results = list.files(results.path)

i = 0
df.subject <- data.frame()
df.trials <- data.frame()
df.attention <- data.frame()
for (anon_result in anon_results) {
  
  result_json = fromJSON(paste(results.path, anon_result, sep =""))

  df.attention = bind_rows(
    df.attention, 
    data.frame(
      workerid = i,
      sound_check = result_json$answers$sound_check,
      attention_check = result_json$answers$attention_check,
      utterance = result_json$answers$trials$utteranceType
    )
  )
  
  df.subject = bind_rows(
    df.subject, 
    data.frame(result_json$answers$subject_information) %>% mutate(workerid = i)
  )
  
  df.trials = bind_rows(
    df.trials, 
    result_json$answers$trials %>% select(-events, -testResults) %>% mutate(workerid = i)
  )

  i = i + 1
}
```



```{r}
failed.attention <- c(0, 3, 4, 8, 9, 11, 15, 16, 24, 28, 33, 35, 47, 49, 57, 58, 61, 73, 74, 80, 95, 100, 106)
wrong.or.confused <- c(0, 23, 25,  32, 37, 42, 40, 52, 57, 63, 69, 73, 96, 100, 106, 107)
non.english <- c(81, 92)
```

Subject 29 didn't report a language.


```{r}
df.trials <- df.trials %>%
  mutate(fail_attention = workerid %in% failed.attention,
         non_english = workerid %in% non.english,
         pass = !(workerid %in% c(failed.attention, non.english)),
         genericEndorsement = ifelse(genericEndorsement == "Yes", 1, 0),
         utteranceType = ifelse(utteranceType == "barePlural", 
                                "generic", "specific")) %>%
  rename(trialNum = id)
```


#### Number of subjects

```{r echo = T}
df.trials %>%
  group_by(utteranceType, pass) %>%
  count() %>%
  kable()
```




## Free response data (with other data)


Explanation of columns:

- pass = passed attention checks
- worked = did the blickets you tested squeak?
- reasoning = why or why not?
- n = number of items tested
- t = time exploring (in minutes)
- prob = probability that next blicket will squeak
- gen = "Blickets squeak" true or false?
- teach = what would you tell the children?

```{r, echo = F}
df.trials %>%
  select(workerid, utteranceType, pass, notebook, featureAgreement, reasoning, itemsTested, timeExploring,  probabilityOfFeature, genericEndorsement, freeResponse) %>%
  rename( utterance = utteranceType,
          subj = workerid,
          worked = featureAgreement,
          teach = freeResponse,
          prob = probabilityOfFeature,
         gen = genericEndorsement,
         n = itemsTested, 
         t = timeExploring) %>%
    mutate(t = round(t, 2)) %>%
  kable()
```


```{r eval = F}
df.trials %>%
  filter(pass) %>%
  ggplot(., aes( x = timeExploring))+
  geom_histogram( bins = 30)
```

## Time exploring

```{r}
df.trials %>%
  filter(!fail_attention, !non_english) %>%
  ggplot(., aes( x = timeExploring)) +
  geom_histogram( bins = 30) +
  facet_grid(utteranceType ~ .)
  #xlim(0, 2)

#ggsave(paste(fig.path, "time_exploring_alt.pdf", sep = ""), width = 5, height = 3.5)

```

## Objects tested

```{r}
fig.obj <- df.trials %>%
  filter(!fail_attention, !non_english) %>%
  ggplot(., aes( x = itemsTested))+
  geom_bar()+
  facet_grid(utteranceType ~ .)
fig.obj
#ggsave(fig.obj, paste(fig.path, "obj_tested_alt.pdf", sep = ""), width = 5, height = 3.5)
```

## Probability judgment

```{r}
df.trials %>%
  filter(!fail_attention, !non_english) %>%
  ggplot(., aes( x = probabilityOfFeature))+
  geom_histogram()+
  facet_grid(utteranceType ~ .)+
  xlab("Probability judgment")

#ggsave(paste(fig.path, "prob_judgment_alt.pdf", sep = ""), width = 5, height = 3.5)
```

## Items tested vs. probability judgment

```{r}
df.trials %>%
  filter(!fail_attention, !non_english) %>%
  ggplot(., aes( x = itemsTested, y = probabilityOfFeature, color = utteranceType,
                 label = workerid))+
  #geom_point()+
  geom_text()+
  scale_color_solarized()+
  ylab("Probability judgment")+
  xlab("number of items tested")+
  coord_fixed(ratio = 40)

#ggsave(paste(fig.path, "prob_vs_nItems_alt.pdf", sep = ""), width = 5, height = 4)
```

```{r}
df.bs <- df.trials %>%
  filter(!fail_attention, !non_english) %>%
  # select(-freeResponse) %>%
  gather(key, val, itemsTested, timeExploring, probabilityOfFeature, genericEndorsement) %>%
  group_by(key, utteranceType, proportionSuccess) %>%
  tidyboot_mean(column = val)
```

## All measures (means and 95% CI)

```{r}
df.bs %>% 
  ggplot(., aes( x = factor(proportionSuccess), fill = utteranceType,
                 y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_col(position = position_dodge(1), color = 'black')+
  geom_errorbar(position = position_dodge(1), width =0.5)+
  scale_fill_solarized()+
  facet_wrap(~key, scales = 'free')+
  xlab("true probability")

#ggsave(paste(fig.path, "bootstrapped_measures_alt.pdf", sep = ""), width = 6, height = 4)

```
