---
title: "Analysis of pilot data 6 for genex"
output: github_document
---

[Link to expt](https://www.mit.edu/~karengu//category-experiment/template/template.html)
[Other condition](https://www.mit.edu/~karengu/category-experiment2/category-experiment/template/template.html)

```{r, echo = F}
knitr::opts_chunk$set(echo = F, warning = F, fig.width = 6,
                      fig.height =4, fig.asp = 0.5)
library(knitr)
library(ggthemes)
library(tidyboot)
library(jsonlite)
library(tidyverse)
theme_set(theme_few())
results.path <- "../results/anon_results_v6/"
# fig.path <- "~/projects/negant/"
```

```{r, echo=F, warning=F}

anon_results = list.files(results.path)

i = 0
df.subject <- data.frame()
df.trials <- data.frame()
df.attention <- data.frame()
for (anon_result in anon_results) {
  
  result_json = fromJSON(paste(results.path, anon_result, sep =""))

  df.attention = bind_rows(
    df.attention, 
    data.frame(
      workerid = i,
      sound_check = result_json$answers$sound_check,
      attention_check = result_json$answers$attention_check,
      utterance = result_json$answers$trials$utteranceType,
      notebook = result_json$answers$trials$notebook
    )
  )
  
  df.subject = bind_rows(
    df.subject, 
    data.frame(result_json$answers$subject_information) %>% mutate(workerid = i)
  )
  
  df.trials = bind_rows(
    df.trials, 
    result_json$answers$trials %>% select(-events, -testResults, -notebook) %>% mutate(workerid = i)
  )

  i = i + 1
}
```



```{r}
# "all": 1, 52, 119, 121, 129, 149
# no mention of ringing: 4, 8, 24, 91
# no mention of squeaking: 35, 66, 90, 124, 140
# specific to generic: 0, 7, 11, 28, 33, 70, 123, 135, 148
# did not attempt to remember utterance: 47, 92, 130, 160
# only specific: 2, 9, 67, 98, 128, 150
# failed sound check: 15, 154
# do not ring: 17, 63, 117
# "if it squeaks, it rings": 16
# "blickets buzz and ring": 44
# "some": 96, 142
failed.attention <- c(0, 1, 2, 4, 7, 8, 9, 11, 15, 16, 17, 24, 28, 33, 35, 44, 47, 52, 63, 66, 67, 70, 90, 91, 92, 96, 98, 117, 119, 121, 123, 124, 128, 129, 130, 135, 140, 142, 148, 149, 150, 154, 160)
# wrong: 23, 25, 32, 37, 42, 52, 59, 76, 80, 87, 92, 141, 154, 161
# confused: 0, 40, 57, 63, 66, 73, 81, 91, 132, 160
wrong.or.confused <- c(0, 23, 25, 32, 37, 40, 42, 52, 57, 59, 62, 66, 76, 80, 81, 87, 91, 92, 132, 141, 154, 160, 161)
# confused static with ringing: 49
bad.reasoning <- c(49)
special.blicket <- c(5, 6, 10, 13, 16, 27, 29, 30, 41, 55, 72, 73, 76, 90, 92, 97, 98, 99, 101)
low.probability <- c(1, 9, 12, 20, 31, 33, 37, 45, 52, 53, 56, 58, 60, 61, 65, 68, 70, 75, 79, 88, 91, 94, 96)
special.conditions <- c(0, 59, 63, 64, 81, 104, 105) # includes blickets are defective or different
speaker.error <- c(2, 11, 18, 19, 21, 22, 26, 32, 34, 39, 44, 46, 48, 67, 69, 82, 84, 95, 103) # includes that the box was not really blickets
other <- c(3, 4, 7, 8, 17, 23, 24, 25, 28, 35, 36, 38, 40, 42, 43, 47, 50, 51, 54, 57, 62, 66, 71, 74, 77, 78, 80, 83, 85, 86, 87, 89, 93, 100, 102, 106, 107)
# spanish/french: 108
# no language: 123, 126, 137
# spanish: 99, 131
# "united states": 75, 76
non.english <- c(75, 76, 81, 99, 108, 123, 126, 131, 137)

# did not fill out last slide at all: 123, 126
```

```{r}
df.trials <- df.trials %>%
  mutate(fail_attention = workerid %in% failed.attention,
         non_english = workerid %in% non.english,
         wrong_confused = workerid %in% wrong.or.confused,
         pass = !(workerid %in% c(failed.attention, non.english, wrong.or.confused)))
df.trials <- df.trials %>% mutate(genericEndorsement = ifelse(genericEndorsement == "Yes", 1, 0),
         utteranceType = ifelse(utteranceType == "barePlural", 
                                "generic", "specific")) %>%
  rename(trialNum = id)
```


#### Number of subjects

```{r echo = T}
num.subjects <- df.trials %>%
  group_by(utteranceType, pass) %>%
  count()
num.subjects %>% 
  kable()
```

### Reasoning type

```{r}
df.trials <- df.trials %>%
  mutate(reasoningType = ifelse(workerid %in% special.blicket, "specialBlicket",
                                ifelse(workerid %in% low.probability, "lowProb",
                                       ifelse(workerid %in% special.conditions, "specialCond",
                                              ifelse(workerid %in% speaker.error, "speakerErr", "other")))))
reasoning <- df.trials %>%
  group_by(utteranceType, reasoningType) %>%
  count()
reasoning %>%
  kable()
```


## Free response data (with other data)


Explanation of columns:

- pass = passed attention checks
- worked = did the blickets you tested squeak?
- reasoning = why or why not?
- n = number of items tested
- t = time exploring (in minutes)
- prob = probability that next blicket will squeak
- gen = "Blickets squeak" true or false?
- teach = what would you tell the children?

```{r, echo = F}
df.trials.pretty <- df.trials %>%
  select(workerid, utteranceType, pass, featureAgreement, reasoning, itemsTested, timeExploring,  probabilityOfFeature, genericEndorsement, freeResponse) %>%
  rename( utterance = utteranceType,
          subj = workerid,
          worked = featureAgreement,
          teach = freeResponse,
          prob = probabilityOfFeature,
         gen = genericEndorsement,
         n = itemsTested, 
         t = timeExploring) %>%
    mutate(t = round(t, 2))
df.trials.pretty %>%
  kable()
```


```{r eval = F}
df.trials %>%
  filter(pass) %>%
  ggplot(., aes( x = timeExploring))+
  geom_histogram( bins = 30)
```

## Time exploring

```{r}
df.trials %>%
  filter(pass) %>%
  ggplot(., aes( x = timeExploring)) +
  geom_histogram( bins = 30) +
  facet_grid(utteranceType ~ .)
  #xlim(0, 2)

#ggsave(paste(fig.path, "time_exploring_alt.pdf", sep = ""), width = 5, height = 3.5)

```

## Objects tested

```{r}
fig.obj <- df.trials %>%
  filter(pass) %>%
  ggplot(., aes( x = itemsTested))+
  geom_bar()+
  facet_grid(utteranceType ~ .)
fig.obj
#ggsave(fig.obj, paste(fig.path, "obj_tested_alt.pdf", sep = ""), width = 5, height = 3.5)
```

## Probability judgment

```{r}
df.trials %>%
  filter(pass) %>%
  ggplot(., aes( x = probabilityOfFeature))+
  geom_histogram()+
  facet_grid(utteranceType ~ .)+
  xlab("Probability judgment")

#ggsave(paste(fig.path, "prob_judgment_alt.pdf", sep = ""), width = 5, height = 3.5)
```

## Items tested vs. probability judgment

```{r}
df.trials %>%
  filter(pass) %>%
  ggplot(., aes( x = itemsTested, y = probabilityOfFeature, color = utteranceType,
                 label = workerid))+
  geom_point()+
  #geom_text()+
  scale_color_solarized()+
  ylab("Probability judgment")+
  xlab("number of items tested")+
  coord_fixed(ratio = 30)

#ggsave(paste(fig.path, "prob_vs_nItems_alt.pdf", sep = ""), width = 5, height = 4)
```

```{r}
df.bs <- df.trials %>%
  filter(pass) %>%
  #select(-freeResponse) %>%
  gather(key, val, itemsTested, timeExploring, probabilityOfFeature, genericEndorsement) %>%
  group_by(key, utteranceType, proportionSuccess) %>%
  tidyboot_mean(column = val)
```

## All measures (means and 95% CI)

```{r}
df.bs %>% 
  ggplot(., aes( x = factor(proportionSuccess), fill = utteranceType,
                 y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_col(position = position_dodge(1), color = 'black')+
  geom_errorbar(position = position_dodge(1), width =0.5)+
  scale_fill_solarized()+
  facet_wrap(~key, scales = 'free')+
  xlab("true probability")

#ggsave(paste(fig.path, "bootstrapped_measures_alt.pdf", sep = ""), width = 6, height = 4)

```
